\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\title{CSC 349-01: Design and Analysis of Algorithms Fall 2021}
\author{Lecture 30: December 3rd, 2021}
\begin{document}

\maketitle{Scribe: Harsimran Preet Singh\\* Instructor: Theresa Migler}
\documentclass{}

\section{Announcements}

None

\section{Approximation Algorithm for Bin Packing}

\subsection{General Idea for Approximation Algorithms}
Main idea is to find fast algoritms that produce feasible solutions that are probably close to optimal.

\subsection{Pseudocode for Bin Packing}
\noindent\fbox{%
    \parbox{\textwidth}{%
        \textbf{Input}: \textit{n} items each with a weight wi ≤1 and an unlimited supply of unit capacity bins,\textit{ b1,b2,....}\\
        \textbf{Goal}: An assignment of items to bins such that the bin capacity is not exceeded and the minimum number of bins is used.
        
    }%
}
Example:

\begin{itemize}
\item Suppose we are given 7 items with weights:{.3,.2,.2,.2,.2,.4,.5}
\item \textit{b1} = {1,2,3,4},\textit{ b2} = {5,6}, and \textit{b3} = {7} is a feasible assignment.
\item Is it optimal? Ans: No, we can do better.
\item How about \textbf{b1} = {2,3,4,6} and \textit{b2} = {1,5,7}?
\end{itemize}

\noindent\rule[0.5ex]{\linewidth}{1pt}
FirstFit(\{\textit{w1,w2,w3,...wn}\})
\newline
\noindent\rule[0.5ex]{\linewidth}{1pt}
\textbf{Input}: \textit{n} items each with a weight wi ≤ 1 and an unlimited supply of unit capacity bins,\textit{ b1,b2,....}
\newline
\textbf{Output}: An assignment of items to bins such that the bin capacity is not exceeded and the minimum number of bins is used.
\begin{enumerate}
\item \textbf{for} i from 1 to n \textbf{do}
\item \tab Suppose the first x bins are partially filled.
\item \tab \textbf{for} j from 1 to x \textbf{do}
\item \tab \tab \textbf{if} Item i fits into bin j \textbf{then}
\item \tab \tab Add item i to bin j
\item \tab \textbf{if} Item i has not been assigned \textbf{then}
\item \tab \tab Start a new bin, bx +1 and add item i to it.
\end{enumerate}

\newline
\noindent\rule[0.5ex]{\linewidth}{1pt}
\subsection{Things to note about the above Algorithm }
\begin{itemize}
\item Every item gets assigned a bin.
\item The capacity constraint for each bin is met
\item \textbf{FirstFit} produces a feasible solution
\end{itemize}


\subsection{Feasibility of FirstFit(\{w1,w2,w3,...wn\})}

\noindent\fbox{%
    \parbox{\textwidth}{%
        \textbf{Lemma}: \textit{returns} a proper bin packing (no bin has more than 1 unit of weight assigned to it).
        \newline \newline
        \textbf{Proof}: We can see in line 4 of FirstFit({\{w1,w2,w3,...wn \}}) that we only add item i to bin j if it fits (if it doesn’t exceed the unit capacity of bin j ).
        
    }%
}
\begin{itemize}
\item What is the running time of FirstFit(\{w1,w2,w3,...wn\})? \textbf{O(n^2)}
\item  
\item FirstFit produces a feasible solution.  
\item \tab Is it optimal? \textbf{ NO (example where it wont work is with inputs: .5, .6, .2, .5)} 
\item How Close to OPT? 
\item Note: If on completion of \textbf{First Fit}, there are \textit{m} bins used, then at least \textit{m-1} bins are more than half filled.
\item Thus:
\end{itemize}
\begin{equation} \label{eq1}
\begin{split}
OPT \geq \sum_{i=1}^{n} wi > \frac{1}{2}(m-1) 
\end{split}
\end{equation}

\begin{equation} 
\begin{split}
So, 2OPT > m-1
\end{split}
\end{equation}
and OPT and \textit{m} are both integers so: \\
\noindent\fbox{%
    \parbox{\textwidth}{%
        \begin{equation}
        \begin{split}
        2OPT > m \geq OPT
        \end{split}
        \end{equation}
        
    }%
}


\end{document}